Dynamic Modeling, Parameter Estimation and Uncertainty Analysis in \proglang{R}

### 2017-07-18 article.tex
Add file with R source code

%% almost as usual
\author{Daniel Kaschek\\University of Freiburg \And
	Marcus Rosenblatt\\University of Freiburg \AND
	Wolfgang Mader\\University of Freiburg \And
	Mirjam Fehling-Kaschek\\University of Freiburg \And
	Jens Timmer\\University of Freiburg}

@@

The \pkg{dMod} package is available on the Comprehensive \proglang{R} Archive Network at \url{http://CRAN.R-project.org/package=dMod}. The project is hosted on GitHub, \url{https://github.com/dkaschek/dMod}, where the most recent development version is available.

>>>>

%% almost as usual
\author{Daniel Kaschek\\University of Freiburg \And
	Wolfgang Mader\\University of Freiburg \AND
	Mirjam Fehling-Kaschek\\University of Freiburg \And
	Marcus Rosenblatt\\University of Freiburg \And
	Jens Timmer\\University of Freiburg}

@@

The \pkg{dMod} package is available on the Comprehensive \proglang{R} Archive Network at \url{http://CRAN.R-project.org/package=dMod}. The project is hosted on GitHub, \url{https://github.com/dkaschek/dMod}, where the most recent development version is available. \pkg{dMod} is licensed under the GPL-3 license.
